---
title: "Mask Wearing & Vaccine Hesitancy: Figures for Paper (Waves 5-7)"
subtitle: Interaction Figures
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 4
params:
  stargazer_type: "latex" # text, latex
  save_tex: true
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      message=FALSE, 
                      warning=FALSE)
```

```{r}
filepath_replication_data <- '[ENTER DIRECTORY HERE]'
```

```{r lib, message=FALSE}
library(scales)
library(tidyverse)
library(lfe)
library(knitr)
library(haven)
library(broom)
library(knitr)
library(kableExtra)
library(gridExtra)
library(ggpubr)
```

```{r source_scripts}
source("helper-objects.R")
source("helper-functions.R")
```

```{r LOAD_SURVEY_DATA_dat, message=FALSE}
dat <- read_dta(file.path(filepath_replication_data, 
                          'final_replication_survey_dataset.dta')) %>% 
  rename(Q147_would_get_covid_vaccine_yes_binary   = Q147_would_get_covid_vaccine_yb,
         Q146_flu_vaccine_2020_yes_binary          = Q146_flu_vaccine_2020_yes_binar,
         zip_hh_inc_2018_median_range_middle       = zip_hh_inc_2018_median_range_mi, 
         zip_educ_2018_high_school_or_less         = zip_educ_2018_high_school_or_le, 
         demo_household_income_range_middle        = demo_household_income_range_mid,
         demo_race_ethnicity_binned_hispanic       = demo_race_ethnicity_binned_hisp,
         demo_household_income_top_quartile_binary = demo_household_income_top_quart,
         zip_hh_inc_2018_prop_top_quartile         = zip_hh_inc_2018_prop_top_quarti,
         Q10x_plan_tried_vaccinated_binary         = Q10x_plan_tried_vaccinated_bina
          ) %>% 
  mutate_if(is.labelled, as_factor)
```

```{r data_for_model_list}
data_for_model_list <- dat %>% 
  # Make long
  pivot_longer(cols = c("Q31_mask_wearing_always_binary", 
                        "Q146_flu_most_recent_yes_binary",
                        "Q10x_dose_vaccine_binary",
                        "Q10x_plan_tried_vaccinated_binary"),
               names_to = "dv_name", 
               values_to = "dv_value")
```

```{r dat_long_dvs}
dat_long_dvs <- dat %>% 
  select(
    weights,
    wave,
    demo_zip_scrambled,
    prop_r,
    # DVs
    Q31_mask_wearing_always_binary,
    Q146_flu_most_recent_yes_binary,
    Q10x_dose_vaccine_binary,
    Q10x_plan_tried_vaccinated_binary,
    # IVs
    party_with_independents
  ) %>% 
  gather(key = dv_name, value = dv_value, 
         Q31_mask_wearing_always_binary,
         Q146_flu_most_recent_yes_binary,
         Q10x_dose_vaccine_binary,
         Q10x_plan_tried_vaccinated_binary,
         ) %>% 
    mutate(dv_name_original = dv_name,
         dv_name          = str_remove(dv_name, "^Q[0-9]*_"),
         dv_name          = str_remove(dv_name, "_binary$"),
         dv_name          = str_remove(dv_name, "^activity_")) 
```

\pagebreak

```{r dv_name_vec_four_primary}
dv_name_vec_four_primary <- c(
  "Q31_mask_wearing_always_binary" = "Always Wear Mask",
  "Q10x_plan_tried_vaccinated_binary" = "\\shortstack{COVID Vaccine\\\\ (Intends to Vaccinate\\\\ or Already Vaccinated)}",
  "Q146_flu_most_recent_yes_binary" = "\\shortstack{Flu Vaccine\\\\ (Most Recent)}"
)
```

```{r}
dv_name_vec_2021_only <- c(
  "Q31_mask_wearing_always_binary" = "Always Wear Mask",
  "Q10x_plan_tried_vaccinated_binary" = "\\shortstack{COVID Vaccine\\\\ (Intends to Vaccinate\\\\ or Already Vaccinated)}",
  "Q10x_dose_vaccine_binary"          = "\\shortstack{COVID Vaccine\\\\ (Already Vaccinated)}",
  "Q146_flu_most_recent_yes_binary" = "\\shortstack{Flu Vaccine\\\\ (Most Recent)}"
)
```

```{r remove_objects_for_memory_reasons, eval=FALSE}
# remove objects that aren't needed. R may run out of space fast
ls_object_class <- ls() %>% 
  set_names(., .) %>% 
  map( ~ class(get(.)))

ls_object_class_df <- ls_object_class %>% 
  keep( ~ any(. == "data.frame"))

rm_keep_these_df <- c(
  "data_for_model_list",
  "df_display_names_regressions"
)

rm(list = setdiff(names(ls_object_class_df), rm_keep_these_df))
res_gc <- purrr::quietly(gc)()
```

# GOP Interactions: 2020 - 2021

## Run Model

```{r formula_zc_interactions_white_college_income}
formula_zc_interactions_white_college_income <- 
  dv_value ~ republican + 
             republican:prop_r + 
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             log(deaths_14_days_county_pc_1k + 0.1) +
             # Time Fixed Effects
             as.factor(wave) +
             # Individual Controls
             factor(demo_gender) +
             demo_household_income_range_middle +
             demo_household_income_missing +
             as_factor(demo_education_binned) +
             demo_age +
             demo_race_ethnicity_binned_hispanic +
             Q7_health_dx_sum | 
             # FE + SE
             demo_zip_scrambled | 0 | demo_zip_scrambled
```

```{r model_zc_interactions_white_college_income}
model_zc_interactions_white_college_income <- data_for_model_list %>%
  # Run models
  split(.$dv_name) %>% 
  map( ~ felm(data = drop_na(., party),
              weights = drop_na(., party)$weights,
              formula = formula_zc_interactions_white_college_income))
```

## Save Tex File - All Coefficients (Table S2)

```{r model_zc_interactions_white_college_income_kable_ready}
model_zc_interactions_white_college_income_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = model_zc_interactions_white_college_income,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_four_primary
  )
```

```{r model_zc_interactions_white_college_income_kable_fe_info}
model_zc_interactions_white_college_income_kable_fe_info <- create_kable_felm(
  data = model_zc_interactions_white_college_income_kable_ready,
  dv_name_vec = dv_name_vec_four_primary,
  input_term_names = df_display_names_regressions, 
  packed_rows = FALSE, 
  escape_first_space = TRUE,
  caption = "Within-ZIP Code Models of Neighborhood Partisanship (All Coefficients, Waves 1 to 7)",
  fixed_effect_info = list(
    vars = names(dv_name_vec_four_primary),
    fe   = c("\\ ZIP Code Fixed Effect"),
    cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
  )
)
```

```{r SAVE_model_zc_interactions_white_college_income_kable_fe_info}
save_kable(
  x = model_zc_interactions_white_college_income_kable_fe_info,
  file = "tex-files/model_zc_interactions_white_college_income_kable_fe_info - ALL WAVES.tex"
)
```

# GOP Interactions: 2021 Only

## Run Model

```{r model_zc_interactions_white_college_income_2021_ONLY}
model_zc_interactions_white_college_income_2021_ONLY <- data_for_model_list %>%
  filter(wave %in% 5:7) %>% 
  # Run models
  split(.$dv_name) %>% 
  map( ~ felm(data = drop_na(., party),
              weights = drop_na(., party)$weights,
              formula = formula_zc_interactions_white_college_income))
```

## Save Tex File - All Coefficients (Table S4)

```{r model_zc_interactions_white_college_income_2021_ONLY_kable_ready}
model_zc_interactions_white_college_income_2021_ONLY_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = model_zc_interactions_white_college_income_2021_ONLY,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_2021_only
  )
```

```{r model_zc_interactions_white_college_income_2021_ONLY_kable_fe_info}
model_zc_interactions_white_college_income_2021_ONLY_kable_fe_info <- create_kable_felm(
  data = model_zc_interactions_white_college_income_2021_ONLY_kable_ready,
  dv_name_vec = dv_name_vec_2021_only,
  input_term_names = df_display_names_regressions, 
  packed_rows = FALSE, 
  escape_first_space = TRUE,
  caption = "Within-ZIP Code Models of Neighborhood Partisanship (2021 Only)",
  fixed_effect_info = list(
    vars = names(dv_name_vec_2021_only),
    fe   = c("\\ ZIP Code Fixed Effect"),
    cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
  )
)
```

```{r SAVE_model_zc_interactions_white_college_2021_ONLY_income_kable_fe_info}
save_kable(
  x = model_zc_interactions_white_college_income_2021_ONLY_kable_fe_info,
  file = "tex-files/model_zc_interactions_white_college_income_2021_ONLY_kable_fe_info - 2021 ONLY.tex"
)
```


# GOP Interactions + Mask Policy Interaction

```{r}
dv_name_vec_mask_policy <- c(
  "no_mask_policy" = "\\shortstack{Always Wear\\\\ Mask}",
  "mask_policy" = "\\shortstack{Always Wear Mask\\\\ (Policy Added)}",
  "mask_policy_interactions" = "\\shortstack{Always Wear Mask\\\\ (Policy Interaction)}"
)
```


## Run the Models

```{r formula_zc_interactions_white_college_income_MASK_POLICY}
formula_zc_interactions_white_college_income_MASK_POLICY <- 
  dv_value ~ republican + 
             republican:prop_r + 
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             log(deaths_14_days_county_pc_1k + 0.1) +
             mask_policy_active + 
             # Time Fixed Effects
             as.factor(wave) +
             # Individual Controls
             factor(demo_gender) +
             demo_household_income_range_middle +
             demo_household_income_missing +
             as_factor(demo_education_binned) +
             demo_age +
             demo_race_ethnicity_binned_hispanic +
             Q7_health_dx_sum | 
             # FE + SE
             demo_zip_scrambled | 0 | demo_zip_scrambled
```

```{r formula_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS}
formula_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS <- 
  dv_value ~ republican + 
             republican:prop_r + 
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             log(deaths_14_days_county_pc_1k + 0.1) +
             mask_policy_active + 
             republican:mask_policy_active +
             prop_r:mask_policy_active +
             republican:prop_r:mask_policy_active + 
             # Time Fixed Effects
             as.factor(wave) +
             # Individual Controls
             factor(demo_gender) +
             demo_household_income_range_middle +
             demo_household_income_missing +
             as_factor(demo_education_binned) +
             demo_age +
             demo_race_ethnicity_binned_hispanic +
             Q7_health_dx_sum | 
             # FE + SE
             demo_zip_scrambled | 0 | demo_zip_scrambled
```

```{r model_zc_interactions_white_college_income_NO_MASK_POLICY_WAVES_1_AND_2}
model_zc_interactions_white_college_income_NO_MASK_POLICY_WAVES_1_AND_2 <- data_for_model_list %>%
  # Just the mask variable, only first two waves
  filter(dv_name == "Q31_mask_wearing_always_binary",
         wave %in% 1:2) %>% 
  # Run models
  split(.$dv_name) %>% 
  map( ~ felm(data = drop_na(., party),
              weights = drop_na(., party)$weights,
              formula = formula_zc_interactions_white_college_income))
```

```{r model_zc_interactions_white_college_income_MASK_POLICY}
model_zc_interactions_white_college_income_MASK_POLICY <- data_for_model_list %>%
  # Just the mask variable, only first two waves
  filter(dv_name == "Q31_mask_wearing_always_binary",
         wave %in% 1:2) %>% 
  # Run models
  split(.$dv_name) %>% 
  map( ~ felm(data = drop_na(., party),
              weights = drop_na(., party)$weights,
              formula = formula_zc_interactions_white_college_income_MASK_POLICY))
```

```{r model_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS}
model_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS <- data_for_model_list %>%
  # Just the mask variable, only first two waves
  filter(dv_name == "Q31_mask_wearing_always_binary",
         wave %in% 1:2) %>% 
  # Run models
  split(.$dv_name) %>% 
  map( ~ felm(data = drop_na(., party),
              weights = drop_na(., party)$weights,
              formula = formula_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS))
```

## Save Tex File - All Coefficients  (Table S6)

```{r model_zc_interactions_white_college_income_MASK_POLICY_kable_ready}
model_zc_interactions_white_college_income_MASK_POLICY_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = set_names(model_zc_interactions_white_college_income_NO_MASK_POLICY_WAVES_1_AND_2,
                                 "no_mask_policy") %>% 
      append(set_names(model_zc_interactions_white_college_income_MASK_POLICY,
                       "mask_policy")) %>% 
      append(set_names(model_zc_interactions_white_college_income_MASK_POLICY_INTERACTIONS,
                       "mask_policy_interactions"))
    ,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_mask_policy
  )
```

```{r model_zc_interactions_white_college_income_MASK_POLICY_kable_fe_info}
model_zc_interactions_white_college_income_MASK_POLICY_kable_fe_info <- create_kable_felm(
  data = model_zc_interactions_white_college_income_MASK_POLICY_kable_ready,
  dv_name_vec = dv_name_vec_mask_policy,
  input_term_names = df_display_names_regressions, 
  packed_rows = FALSE, 
  escape_first_space = TRUE,
  caption = "Adding Mask Policies to Within-ZIP Code Models (May and July 2020)",
  fixed_effect_info = list(
    vars = names(dv_name_vec_mask_policy),
    fe   = c("\\ ZIP Code Fixed Effect"),
    cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
  )
)
```

```{r}
save_kable(
  x = model_zc_interactions_white_college_income_MASK_POLICY_kable_fe_info,
  file = "tex-files/model_zc_interactions_white_college_income_MASK_POLICY_kable_fe_info_WAVES_1_TO_2_VAXX.tex"
)

```

# Within-County Models

## Pooled Model (GOP * All Share Variables)

### Run Model

```{r formula_county_interactions_white_college_income}
formula_county_interactions_white_college_income <- 
  dv_value ~ republican + 
             prop_r + 
             republican:prop_r +
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             log(deaths_14_days_county_pc_1k + 0.1) + 
             # Time fixed effects
             as.factor(wave) + 
             # Individual Controls
             factor(demo_gender) + 
             demo_household_income_range_middle + 
             demo_household_income_missing +      
             as_factor(demo_education_binned) + 
             demo_age + 
             demo_race_ethnicity_binned_hispanic + 
             Q7_health_dx_sum + 
             # Zipcode controls
             zip_pop_density_2018_over_2010 + 
             zip_educ_2018_college_and_above + 
             zip_white + 
             zip_hh_inc_2018_median_range_middle |   
             # FE + SE
             county_modified | 0 | demo_zip_scrambled
```

```{r model_county_interactions_white_college_income}
model_county_interactions_white_college_income <- data_for_model_list %>% 
  filter(!is.na(party)) %>% 
  # Run Models
  split(.$dv_name) %>% 
  map( ~ felm(data = .,
              weights = .$weights,
              formula = formula_county_interactions_white_college_income))
```

### Save Tex File - All Coefficients (Table S1)

```{r model_county_interactions_white_college_income_kable}
model_county_interactions_white_college_income_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = model_county_interactions_white_college_income,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_four_primary
  )
```

```{r model_county_interactions_white_college_income_kable_fe_info}
model_county_interactions_white_college_income_kable_fe_info <-
  model_county_interactions_white_college_income_kable_ready %>% 
  create_kable_felm(
    data = .,
    dv_name_vec = dv_name_vec_four_primary,
    input_term_names = df_display_names_regressions,
    packed_rows = FALSE,
    escape_first_space = TRUE,
    caption = "Within-County Models of Neighborhood Partisanship (All Coefficients, Waves 1 - 7)",
    fixed_effect_info = list(
      vars = names(dv_name_vec_four_primary),
      fe   = c("\\ County Fixed Effect"),
      cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
    )
  )
```

```{r}
if (params$save_tex) {
  save_kable(
    x = model_county_interactions_white_college_income_kable_fe_info,
    file = "tex-files/model_county_interactions_white_college_income_kable_fe_info - ALL WAVES.tex"
  )
}
```

## Pooled Model (GOP * All Share Variables): 2021 Only

### Run Model

```{r model_county_interactions_white_college_income_2021_ONLY}
model_county_interactions_white_college_income_2021_ONLY <- data_for_model_list %>% 
  filter(wave %in% 5:7) %>% 
  filter(!is.na(party)) %>% 
  # Run Models
  split(.$dv_name) %>% 
  map( ~ felm(data = .,
              weights = .$weights,
              formula = formula_county_interactions_white_college_income))
```

### Save Tex File - All Coefficients (Table S3)

```{r model_county_interactions_white_college_income_2021_ONLY_kable}
model_county_interactions_white_college_income_2021_ONLY_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = model_county_interactions_white_college_income_2021_ONLY,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_2021_only
  )
```

```{r model_county_interactions_white_college_income_2021_ONLY_kable_fe_info}
model_county_interactions_white_college_income_2021_ONLY_kable_fe_info <-
  model_county_interactions_white_college_income_2021_ONLY_kable_ready %>% 
  create_kable_felm(
    data = .,
    dv_name_vec = dv_name_vec_2021_only,
    input_term_names = df_display_names_regressions,
    packed_rows = FALSE,
    escape_first_space = TRUE,
    caption = "Within-County Models of Neighborhood Partisanship (2021 Only)",
    fixed_effect_info = list(
      vars = names(dv_name_vec_2021_only),
      fe   = c("\\ County Fixed Effect"),
      cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
    )
  )
```

```{r}
if (params$save_tex) {
  save_kable(
    x = model_county_interactions_white_college_income_2021_ONLY_kable_fe_info,
    file = "tex-files/model_county_interactions_white_college_income_2021_ONLY_kable_fe_info - 2021 ONLY.tex"
  )
}
```


## Mask Policies: Pooled Model (GOP * All Share Variables)

```{r formula_county_interactions_white_college_income_MASK_POLICY}
formula_county_interactions_white_college_income_MASK_POLICY <- 
  dv_value ~ republican + 
             prop_r + 
             republican:prop_r +
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             # Add mask policies
             mask_policy_active + 
             # Continue...
             log(deaths_14_days_county_pc_1k + 0.1) + 
             # Time fixed effects
             as.factor(wave) + 
             # Individual Controls
             factor(demo_gender) + 
             demo_household_income_range_middle + 
             demo_household_income_missing +      
             as_factor(demo_education_binned) + 
             demo_age + 
             demo_race_ethnicity_binned_hispanic + 
             Q7_health_dx_sum +
             # Zipcode controls
             zip_pop_density_2018_over_2010 + 
             zip_educ_2018_college_and_above + 
             zip_white + 
             zip_hh_inc_2018_median_range_middle |     #
             # FE + SE
             county_modified | 0 | demo_zip_scrambled
```

```{r formula_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS}
formula_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS <- 
  dv_value ~ republican + 
             prop_r + 
             republican:prop_r +
             republican:zip_white +
             republican:zip_educ_2018_college_and_above +
             republican:zip_hh_inc_2018_median_range_middle +
             # Add mask policies
             mask_policy_active + 
             republican:mask_policy_active +
             prop_r:mask_policy_active +
             republican:prop_r:mask_policy_active + 
             # Continue...
             log(deaths_14_days_county_pc_1k + 0.1) + 
             # Time fixed effects
             as.factor(wave) + 
             # Individual Controls
             factor(demo_gender) + 
             demo_household_income_range_middle + 
             demo_household_income_missing +      
             as_factor(demo_education_binned) + 
             demo_age + 
             demo_race_ethnicity_binned_hispanic + 
             Q7_health_dx_sum +
             # Zipcode controls
             zip_pop_density_2018_over_2010 + 
             zip_educ_2018_college_and_above + 
             zip_white + 
             zip_hh_inc_2018_median_range_middle |     
             # FE + SE
             county_modified | 0 | demo_zip_scrambled
```

```{r}
model_county_interactions_white_college_income_NO_MASK_POLICY_WAVES_1_AND_2 <- data_for_model_list %>% 
  filter(!is.na(party)) %>% 
  filter(wave %in% 1:2,
         dv_name == "Q31_mask_wearing_always_binary",) %>% 
  # Run Models
  split(.$dv_name) %>% 
  map( ~ felm(data = .,
              weights = .$weights,
              formula = formula_county_interactions_white_college_income))

```


```{r model_county_interactions_white_college_income_MASK_POLICY}
model_county_interactions_white_college_income_MASK_POLICY <- data_for_model_list %>% 
  filter(!is.na(party)) %>% 
  filter(wave %in% 1:2,
         dv_name == "Q31_mask_wearing_always_binary",) %>% 
  # Run Models
  split(.$dv_name) %>% 
  map( ~ felm(data = .,
              weights = .$weights,
              formula = formula_county_interactions_white_college_income_MASK_POLICY))
```

```{r model_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS}
model_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS <- data_for_model_list %>% 
  filter(!is.na(party)) %>% 
  filter(wave %in% 1:2,
         dv_name == "Q31_mask_wearing_always_binary",) %>% 
  # Run Models
  split(.$dv_name) %>% 
  map( ~ felm(data = .,
              weights = .$weights,
              formula = formula_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS))
```

### Save Tex File -  All Coefficients (Table S5)

```{r model_county_interactions_white_college_income_MASK_POLICY_kable_ready}
model_county_interactions_white_college_income_MASK_POLICY_kable_ready <- 
  tidy_felm_prep_kable(
    input_model_list = set_names(model_county_interactions_white_college_income_NO_MASK_POLICY_WAVES_1_AND_2,
                                 "no_mask_policy") %>% 
      append(set_names(model_county_interactions_white_college_income_MASK_POLICY,
                       "mask_policy")) %>% 
      append(set_names(model_county_interactions_white_college_income_MASK_POLICY_INTERACTIONS,
                       "mask_policy_interactions"))
    ,
    input_term_names = df_display_names_regressions,
    dv_name_vec = dv_name_vec_mask_policy
  )
```


```{r model_county_interactions_white_college_income_MASK_POLICY_kable_fe_info}
model_county_interactions_white_college_income_MASK_POLICY_kable_fe_info <-
  model_county_interactions_white_college_income_MASK_POLICY_kable_ready %>% 
  create_kable_felm(
    data = .,
    dv_name_vec = dv_name_vec_mask_policy,
    input_term_names = df_display_names_regressions,
    packed_rows = FALSE,
    escape_first_space = TRUE,
    caption = "Adding Mask Policies to Within-County Models (May and July 2020)",
    fixed_effect_info = list(
      vars = names(dv_name_vec_mask_policy),
      fe   = c("\\ County Fixed Effect"),
      cell_value = "\\ \\ \\ \\ \\ \\ \\checkmark"
    )
  )
```

```{r}
if (params$save_tex) {
  save_kable(
    x = model_county_interactions_white_college_income_MASK_POLICY_kable_fe_info,
    file = "tex-files/model_county_interactions_white_college_income_MASK_POLICY_kable_fe_info_WAVES_1_TO_2_VAXX.tex"
  )
}
```

